Gaussian Processes Autoregressive Models for the Disturbance Storm Time Index

### 2016-04-06 swsc.tex
Subsections added in methodology

\begin{eqnarray}
      \mathbf{x} & \in & \mathbb{R}^d \\
      \mathbf{X} & = & (\mathbf{x}_1, \mathbf{x}_2, \cdots, \mathbf{x}_N) \\
      \mathbf{y} & = & (y_1, y_2, \cdots, y_N) \\
      y & = & f(\mathbf{x}) + \epsilon  \\
      f & \sim & \mathcal{GP}(m(\mathbf{x}), K(\mathbf{x},\mathbf{x}'))  \\
      \left(\mathbf{y} \ \ \mathbf{f_*} \right)^\intercal & \sim & 
\mathcal{N}\left(\mathbf{0}, \left[ \begin{array}{ccc} \mathbf{K}(\mathbf{X}, \mathbf{X}) + \sigma^{2} \mathbf{I} & \mathbf{K}(\mathbf{X}, \mathbf{X_*}) \\ \mathbf{K}(\mathbf{X_*}, \mathbf{X}) & \mathbf{K}(\mathbf{X_*}, \mathbf{X_*}) \end{array} \right ] \right) \\
      \mathbf{f_*}|\mathbf{X},\mathbf{y},\mathbf{X_*} & \sim & \mathcal{N}(\mathbf{\bar{f}_*}, \Sigma_*)  \label{eq:posterior} \\
      \mathbf{\bar{f}_*} & = & \mathbb{E}[\mathbf{f_*}|\mathbf{X},\mathbf{y},\mathbf{X_*}]  \\
      & = & K(\mathbf{X_*},\mathbf{X})^\intercal [K(\mathbf{X},\mathbf{X}) + \sigma^{2} \mathbf{I}]^{-1} \mathbf{y} \\
      \Sigma_* & = & K(\mathbf{X_*}, \mathbf{X_*}) - K(\mathbf{X_*},\mathbf{X})^\intercal \left(K(\mathbf{X},\mathbf{X}) + \sigma^{2} \mathbf{I}\right)^{-1}K(\mathbf{X},\mathbf{X_*})
\end{eqnarray}

@@

For the success of a Gaussian Process model an appropriate choice of kernel function is paramount. It is important to note that every kernel function generates a \emph{Reproducing Kernel Hilbert Space} (RKHS) of functions, and the nature of the kernel dictates what restrictions exist on the functions belonging to its RKHS. The interested reader is suggested to refer to \cite{Berlinet2004} for a thorough treatment on RKHS and the rich theory behind them.

@@

The RBF kernel is the most commonly used kernel in machine learning, in its core it

@@

\subsection{Optimizing Hyper-parameters}

>>>>

\subsection{Formulation}

\begin{eqnarray}
      \mathbf{x} & \in & \mathbb{R}^d \\
      \mathbf{X} & = & (\mathbf{x}_1, \mathbf{x}_2, \cdots, \mathbf{x}_N) \\
      \mathbf{y} & = & (y_1, y_2, \cdots, y_N) \\
      y & = & f(\mathbf{x}) + \epsilon  \\
      f & \sim & \mathcal{GP}(m(\mathbf{x}), K(\mathbf{x},\mathbf{x}'))  \\
      \left(\mathbf{y} \ \ \mathbf{f_*} \right)^\intercal & \sim & 
\mathcal{N}\left(\mathbf{0}, \left[ \begin{array}{cc} \mathbf{K}(\mathbf{X}, \mathbf{X}) + \sigma^{2} \mathbf{I} & \mathbf{K}(\mathbf{X}, \mathbf{X_*}) \\ \mathbf{K}(\mathbf{X_*}, \mathbf{X}) & \mathbf{K}(\mathbf{X_*}, \mathbf{X_*}) \end{array} \right ] \right)
\end{eqnarray}

\subsection{Inference and Predictions}

\begin{eqnarray}
      \mathbf{f_*}|\mathbf{X},\mathbf{y},\mathbf{X_*} & \sim & \mathcal{N}(\mathbf{\bar{f}_*}, \Sigma_*)  \label{eq:posterior} \\
      \mathbf{\bar{f}_*} & = & \mathbb{E}[\mathbf{f_*}|\mathbf{X},\mathbf{y},\mathbf{X_*}]  \\
      & = & K(\mathbf{X_*},\mathbf{X})^\intercal [K(\mathbf{X},\mathbf{X}) + \sigma^{2} \mathbf{I}]^{-1} \mathbf{y} \\
      \Sigma_* & = & K(\mathbf{X_*}, \mathbf{X_*}) - K(\mathbf{X_*},\mathbf{X})^\intercal \left(K(\mathbf{X},\mathbf{X}) + \sigma^{2} \mathbf{I}\right)^{-1}K(\mathbf{X},\mathbf{X_*})
\end{eqnarray}

@@

For the success of a Gaussian Process model an appropriate choice of kernel function is paramount. It is important to note that every kernel function generates a \emph{Reproducing Kernel Hilbert Space} (RKHS) of functions, and the nature of the kernel dictates what restrictions exist on the functions belonging to its RKHS. The Gaussian Process model essentially uses basis functions from this RKHS to represent the unknown function. The interested reader is suggested to refer to \cite{Berlinet2004} for a thorough treatment on RKHS and the rich theory behind them.

@@

The RBF kernel is the most commonly used kernel in machine learning, in its core it encodes the idea of \emph{smoothness} because functions drawn from its Hilbert space are infinitely differentiable. The RBF kernel is also an example of a \emph{stationary} kernel i.e. its value depends only on $||\mathbf{x} - \mathbf{y}||$. The quantity $\sigma$ is known as the characteristic \emph{length scale} of this kernel, it is a free parameter (also known as hyper-parameter) which must be determined by the modeller, refer to section \ref{sec:hyp} on how suitable values of kernel hyper-parameters.

@@

\subsection{Optimizing Hyper-parameters} \label{sec:hyp}
